Dataflow-Guided Filtering for Efficient and Adjustable Run-Time Monitoring

### 2014-05-29 policies.tex
Edits to dropping policies section.

In order to match an overhead budget, we need to drop a portion of the
monitoring events. In this section, we discuss how this dropping decision is
made. Specifically, we first discuss how to measure the run-time monitoring
overheads and when monitoring events need to be dropped in
Section~\ref{sec:policies.slack}. Next, we investigate how the decision of
which events to drop can create a trade-off between closely matching the
overhead target and the coverage that can be achieved.

@@

The simplest policy for when to drop monitoring events is to drop all monitoring events as
long as slack is less than or equal to zero.  However, this can result in
wasted work. For example, consider the metadata dependence graph shown in
Figure~\ref{fig:drop.dataflow_graph}. Here, an edge from node {\tt A} to node
{\tt B} represents that if event {\tt A} is dropped, then due to its
invalidated metadata, it will cause event {\tt B} to be also dropped. Square
nodes indicate events where monitoring checks are performed. In the
example, suppose that event {\tt E} is meant to perform a check operation but is dropped.
In this situation, the
monitoring operations that were done for events {\tt C} and {\tt D} were wasted
since their results were not used for any monitoring checks.

@@

One method to eliminate this wasted work is to only make dropping decisions at
the root of these metadata flows. That is, we will decide to either monitor or
not monitor an entire metadata flow. We refer to this dropping decision policy
as \emph{source-only dropping} and we refer to the previous policy of 
dropping any event as \emph{unrestricted dropping}.
Figures~\ref{fig:drop.all_drop} and \ref{fig:drop.source_drop} shows a
comparison of where dropping decisions are made for these two policies. Source
dropping will
result in no wasted work. However, because of the coarser-grained decision, it
may be more difficult to closely match overheads. Source dropping is expected
to work well when there are a large number of independent metadata flows.

Another possible method is to make the dropping decisions somewhere in between
source-only dropping and unrestricted dropping. Looking at the graph from 
Figure~\ref{fig:drop.dataflow_graph}, what we would like to do is make a
decision at event {\tt C} whether to perform monitoring on that branch of the
metadata flow. If we choose to perform monitoring, then we want to perform all
monitoring on that flow. Instead, if we choose to drop event {\tt C}, then the
entire flow is dropped with no wasted work. Similarly, dropping event {\tt F}
drops the bottom flow with no wasted work and event {\tt A} can be dropped to
drop the entire shown metadata flow with no wasted work. If the program can be
analyzed or profiled to identify these instructions which, if dropped, lead to
no wasted work, then this information can be used at run-time to minimize the
amount of wasted work. We refer to this policy as \emph{split-point dropping}.
Figure~\ref{fig:drop.min_drop} shows the points were dropping decisions are
made for this policy.
Min-event dropping is a coarser-grained decision than unrestricted dropping, but
finer-grained that source dropping. Thus, its ability to match overheads is
expected to sit between these other two policies. Similarly, there is still a
chance of wasted work due to strange splitting and merging metadata flow graph
shapes, but typically we expect much less wasted work than unrestricted 
dropping. Thus, we expect the coverage achieved by split-point dropping for a
certain overhead to fall between source and unrestricted dropping. These three
dropping policies create a trade-off space between coverage achieved and
ability to match an overhead target which we evaluate in detail in
Section~\ref{sec:evaluation}.

>>>>

Our goal with enabling partial monitoring is to allow for a specified overhead target or budget to be met while maximizing the amount of monitoring performed.
This is done by dynamically dropping a portion of the monitoring operations. In this section, we discuss in detail how this dropping decision is
made. Specifically, we first discuss how to measure the run-time monitoring
overheads and when monitoring events need to be dropped in
Section~\ref{sec:policies.slack}. Next, we investigate trade-offs created by
selecting which events are dropped. Different policies in determining which
events can be dropped create a trade-off between how closely the overhead
budget is met and the monitoring coverage achieved.

@@

The simplest policy for when to drop monitoring events is to drop all monitoring events as
long as slack is less than or equal to zero.  However, this can result in
wasted work. For example, consider the metadata dependence graph shown in
Figure~\ref{fig:drop.dataflow_graph}. Here, an edge from node {\tt A} to node
{\tt B} represents that if event {\tt A} is dropped, then due to its
invalidated metadata, it will cause event {\tt B} to be filtered. Square
nodes indicate events where monitoring checks are performed. In the
example, suppose that event {\tt E} is meant to perform a check operation but is dropped.
In this situation, the
monitoring operations that were done for events {\tt C} and {\tt D} were wasted
since their results were not used for any monitoring checks.

@@

One method to eliminate this wasted work is to only make dropping decisions at
the root of these metadata flows. That is, we will decide to either monitor or
not monitor an entire metadata flow. We refer to this dropping decision policy
as \emph{source-only dropping} and we refer to the previous policy of 
dropping any event as \emph{unrestricted dropping}.
Figures~\ref{fig:drop.all_drop} and \ref{fig:drop.source_drop} show a
comparison of where dropping decisions are made for these two policies. Source
dropping will
result in no wasted work and thus better coverage. However, because of the coarser-grained decision, it
may be more difficult to closely match overheads. Source dropping is expected
to work well when there are a large number of independent metadata flows.

Another possible method is to make the dropping decisions somewhere in between
source-only dropping and unrestricted dropping. From the graph in 
Figure~\ref{fig:drop.dataflow_graph}, we can see that if the dropping
decision is made at event {\tt C} then we can skip event {\tt E} with no wasted
work. If we instead choose to perform monitoring for event {\tt C}, then we want to perform all
monitoring on that flow. Similarly, event {\tt F} creates a decision point for
the bottom flow that will result in no wasted work and dropping event {\tt A}
allows the entire shown metadata flow to be dropped with no wasted work. If the
program can be
analyzed or profiled to identify these instructions which, if dropped, lead to
no wasted work, then this information can be used at run-time to minimize the
amount of wasted work. We refer to this policy as \emph{sub-flow dropping}.
Figure~\ref{fig:drop.min_drop} shows the points were dropping decisions are
made for this policy.
Min-event dropping is a coarser-grained decision than unrestricted dropping, but
finer-grained that source dropping. Thus, its ability to match overheads is
expected to sit between these other two policies. Similarly, there still exists
edge cases where wasted work can occur, but typically we expect much less
wasted work than unrestricted 
dropping. Thus, we expect the coverage achieved by split-point dropping for a
certain overhead to fall between source and unrestricted dropping. These three
dropping policies create a trade-off space between coverage achieved and
ability to match an overhead target.
